Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-09 paper/main.tex
Add table comparing eval for Julia, Javascript, Python and R

%\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\documentclass[acmsmall]{acmart}
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}

@@

>>>>

%\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\documentclass[acmsmall]{acmart}
\usepackage{listings,hyperref,multirow,paralist,xspace,url,wrapfig}
\usepackage{tabularx}
\input{macro}
\newcommand{\mypara}[1]{\medskip\noindent\emph{#1}\xspace}
\newcommand{\NOTE}[1]{{\it Note: #1}\xspace}

@@

\section{Power scale of \eval }

\begin{table}[h]
	\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
		\hline
		& Julia & Javascript & Python & R \tabularnewline
		\hline % lstlinline does not like tabular environments...
		{\eval} & \texttt{eval(expr)} & \texttt{eval(expr)} & \texttt{eval(expr[, globals[, locals]])} &  \texttt{eval(expr[, envir[, enclos]])}  \tabularnewline
		\hline 
		Environments &Global  & Local & Global or local  & Any \tabularnewline
		\hline
	\end{tabularx}
	\caption{Relative power of \eval throughout languages: in which environment it can evaluate its expression.}
\end{table}
